Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-08 ppdp24/examples.tex
checkpoint

\subsection{Example: 2-Party GMW}
\label{section-metalang-gmw}

@@

>>>>

\subsection{2-Party GMW}
\label{section-metalang-gmw}

@@

\subsection{2-Party BDOZ}

\input{bdoz}

\begin{definition}[Cheating Detection]
  Given $\store \in \aruns(\prog)$ with $\iov(\prog) = S \cup V \cup O$,
  let $X_H = \{ x \mid x \in (\houtputs \cup O_H) \wedge x \in \dom(\store) \}$,
  and let $X_C$ be the adversarial inputs to $X_H$.
  Then \emph{cheating is detected} in $\prog$ iff there exists $\sigma'\in \runs(\prog)$
  with $\store_{X_C} = \store'_{X_C}$.  
\end{definition}

\begin{lemma}
  If cheating is detected in $\prog$, then $\prog$ has integrity.
\end{lemma}
